Multiset-trie data structure

### 2023-03-09 tex/tex/s_experiments.tex
update for marked points in the paper (in s_operations.tex and s_experimanets.tex)

The experiment uses the input data for the construction of the given
data structure and the test data for the execution of the operations
on the given data structure. The input data comprises a set of
randomly generated multisets used for the construction of a data
structure. The test data includes the set of multisets together with
the operations that are evaluated. The input and test data were
generated with respect to parameters $\sigma$ and $n$ as presented in
xTable~\ref{t:benchmark}.

\begin{table}[h]
\center
\begin{tabular}{|c|c|}
\hline
$\sigma$ & $n$ \\
\hline
5		& 1\\
\hline
30	& 1 \\
\hline
5		& 3 \\
\hline
15	& 3 \\
\hline
30	& 3 \\
\hline
10	& 10 \\
\hline
\end{tabular}
\caption{Configuration of $\sigma$ and $n$ in benchmark.}
\label{t:benchmark}
\end{table}

We tested all three types of a query on all of the configurations from
Table 1 results in 18 experiments total, i.e., 6 experiments per
query type. In each experiment, we measured the average time consumed
by the data structure to process the query. The results of the exact
search, sub-multiset, and super-multiset search experiments are
presented in tables Table~\ref{t:res_ex}, Table~\ref{t:res_sub} and
Table~\ref{t:res_sup}, respectively.

>>>>

The experiment uses the input data for the construction of the given
data structure and the test data for the execution of the operations
on the given data structure. The input data comprises a set of
randomly generated multisets used for the construction of a data
structure. The test data includes the set of multisets together with
the operations that are evaluated. The input and test data were
generated with respect to parameters $\sigma$ and $n$ as presented in
Table~\ref{t:benchmark}.

\begin{table}[h]
\center
\begin{tabular}{|c|c|}
\hline
$\sigma$ & $n$ \\
\hline
5		& 1\\
\hline
30	& 1 \\
\hline
5		& 3 \\
\hline
15	& 3 \\
\hline
30	& 3 \\
\hline
10	& 10 \\
\hline
\end{tabular}
\caption{Selected values of parameters $\sigma$ and $n$ in Experiment 5.}
\label{t:benchmark}
\end{table}

The three types of query tested on all of the configurations from
Table 1 results in 18 experiments total, i.e., 6 experiments per
query type. In each experiment, we measured the average time consumed
by the data structure to process the query. The results of the exact
search, sub-multiset, and super-multiset search experiments are
presented in tables Table~\ref{t:res_ex}, Table~\ref{t:res_sub} and
Table~\ref{t:res_sup}, respectively.
